A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-05-18 paper/paper.tex
Revert "Remove the funding note for anon review, put it back in later and worry about page layout then"
This reverts commit a9c4b9a91c3e3cce66d213f68d9d871ec69b010f.
Revert "Anonymousify"
This reverts commit 3f2c6bf50f8b99e5abe9ca588507ef697ad93aae.

\title{A Partitioning Algorithm for Maximum Common Subgraph Problems}
\author{The Anonymous Authors of Paper 2431 \\
Academy of Anonymous Academics, Atlantis \\
anonymous@anony.mouse}

% \thanks{This work was supported by a pile of money from a funding agency.}

>>>>

\title{A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work
was supported by the Engineering and Physical Sciences Research Council [grant
numbers EP/K503058/1 and EP/M508056/1]}}
\author{Ciaran McCreesh \and Patrick Prosser \and James Trimble \\
University of Glasgow, Glasgow, Scotland \\
j.trimble.1@research.gla.ac.uk}
